Making Sequential Programs Deterministic

### 2019-04-04 design.tex
Tweaks

\begin{enumerate}
\item
The individual elements retrieved from it have type \<NonDet>.  This
affects access, iteration, searching, etc.
(Rules \rulename{iteration} and \rulename{next element} in Figure~\ref{fig-ordernondet-rules})
\item
Size-related operations return a deterministic result.  This also affects
queries of whether an iterator has more elements.
\item
If the collection is sorted, or its elements are placed in a collection
that does sorting, the result is deterministic.
\end{enumerate}

@@

\begin{figure}
%    $\infer[\rulename{iteration}]
%    {\Gamma \vdash \|y| : \|OrderNonDet\ Iterator|\angles{\tau}}
%    {\Gamma \vdash \|x| : \|OrderNonDet \ C\angles{\tau}|
%    & C \sqsubseteq \|Collection|
%    & \|y = C.iterator()|
%    & \wellformed{\tau}
%    }$

@@

    \rulename{next element}:
    $
    \forallt{kappa\ \beta} \<OrderNonDet>\ \<Iterator>\angles{\kappa \ \beta} \rightarrow
    \<NonDet>\ \beta
    $

@@

\caption{\<OrderNonDet> Collection rules}
\label{fig-ordernondet-rules}
\end{figure}

@@

This section first describes basic polymorphism over type qualifiers and
over basetypes (\cref{sec:basic-polymorphism}).  Then, it describes two
extensions.
One extension resolves \<OrderNonDet> to \<NonDet> or \<Det> where
needed (\cref{polymorphism-up-down}).
The other extension permits use of polymorphic (type) variables without
affecting binding of those variables --- that is, it affects which
instantiation of an abstraction is chosen at a use site 
(\cref{bindings-uses}).

@@

\OurTypeSystem supports parametric
polymorphism~\cite{Abadi:1989:FIM:77350.77373,Plotkin:1993:LPP:645891.671433}
over both classes and methods.
A polymorphic abstraction (a class or method) is written and
typechecked once.
It acts as if it has multiple different types, and each use site is
typechecked using the most specific applicable (instantiated,
non-polymorphic) type.

@@

\todo{Greekify the following}
\begin{itemize}
\item
Type polymorphism has the usual semantics.  For example, the type of the
identity function is $\forallt{\tau} \tau \rightarrow \tau$, which can be
equivalently written as
$\forallt{\kappa \ \beta} \kappa \ \beta \rightarrow \kappa \ \beta$.

>>>>

\begin{enumerate}
\item
The individual elements retrieved from it have type \<NonDet>.  This
affects access, iteration, searching, etc.
(Rules \rulename{iteration} and \rulename{next element} in \cref{fig-ordernondet-rules}.)
\item
Size-related operations return a deterministic result.  This also affects
queries of whether an iterator has more elements.
\item
If the collection is sorted, or its elements are placed in a collection
that does sorting, the result is deterministic.
\end{enumerate}

@@

\begin{figure}
\todo{Give the types for get and set, which are more basic list/array operations,
  at the beginning before iteration.}

%    $\infer[\rulename{iteration}]
%    {\Gamma \vdash \|y| : \|OrderNonDet\ Iterator|\angles{\tau}}
%    {\Gamma \vdash \|x| : \|OrderNonDet \ C\angles{\tau}|
%    & C \sqsubseteq \|Collection|
%    & \|y = C.iterator()|
%    & \wellformed{\tau}
%    }$

@@

    \rulename{next element}:
    $
    \forallt{\kappa\ \beta} \<OrderNonDet>\ \<Iterator>\angles{\kappa \ \beta} \rightarrow
    \<NonDet>\ \beta
    $

@@

\caption{\<OrderNonDet> Collection rules.  $C$ is a collection class.
    These are partial types indicating the methods' behavior on
    \<OrderNonDet> arguments.  Full types are given in \cref{polymorphism}.}
\todo{These should be method names, not rule names, right?  The figure is
  just giving the types of methods.}
\label{fig-ordernondet-rules}
\end{figure}

@@

This section first describes basic polymorphism over type qualifiers and
over basetypes (\cref{sec:basic-polymorphism}).  Then, it describes two
extensions.
One extension resolves \<OrderNonDet> to \<NonDet> or \<Det> where
needed (\cref{polymorphism-up-down}).
The other extension permits use of polymorphic (type) variables without
affecting binding of those variables --- that is, it affects which
instantiation of a (method) abstraction is chosen at a use site
(\cref{bindings-uses}).

@@

\OurTypeSystem supports parametric
polymorphism~\cite{Abadi:1989:FIM:77350.77373,Plotkin:1993:LPP:645891.671433}
over both classes and methods.
A polymorphic abstraction (a class or method) is written and
typechecked once.
It acts as if it has multiple different types, and each use site is
typechecked using the most specific applicable instantiated
non-polymorphic type.

@@

\begin{itemize}
\item
Type polymorphism has the usual semantics.  For example, the type of the
identity function is $\forallt{\tau} \tau \rightarrow \tau$, which can be
equivalently written as
$\forallt{\kappa \ \beta} \kappa \ \beta \rightarrow \kappa \ \beta$.
